Hypertension and microbiome

### 2018-12-31 rrbiome.Rmd
Minimal model

Calculating linear model using binomial variable for exercice and medication

@@

>>>>

Calculating linear model using binomial variable for exercice and medication.

@@

Calculating linear model using minimal variables.

```{r calculate minimal alpha model}
calculateglm(dset.alpha, modelstring = "%s ~ BL_AGE + SEX + diversities_shannon") %>%
    select(response, estimate, std.error, conf.low, conf.high, p.value) %>%
    kable(.)
```
